The Exoplanet Orbit Database \textsc{II}: Updates to exoplanets.org

### 2014-09-26 draft/ms.tex
Fix missing beta Pic b references.
Fix errors in Section 2.2 on mass calculation based on radius.
Revise according to relevant proof corrections.

There are other entities devoted to similar efforts,
including the Extrasolar Planets Encyclopaedia\footnote{See
  \url{http://exoplanet.eu}.}  \citep{Schneider2011} and the NASA
Exoplanet Archive\footnote{See
  \url{http://exoplanetarchive.ipac.caltech.edu}.}
\citep{Akeson2013}.  The natures of these efforts are complementary, and to the
degree that they are redundant provide important cross-checking and
validation.  As described in \cite{Wright2011}, the EOD is
dedicated to cataloging properties of all \emph{robustly-detected} exoplanets with
\emph{well-determined} orbital parameters published in
\emph{peer-reviewed} literature, and providing outstanding data
exploration and visualization tools for these planets.

@@

{\bf KEPID} stands for KEPler ID, which is the integer number assigned
for a Kepler host star. KEPID is only available for unconfirmed
KOI's imported directly from the Exoplanet Archive by the
exoplanets.org backend.

{\bf KOI} stands for Kepler Objects of Interest, which is an object
with transit signals detected by \kepler\ that have not been validated
as being due to exoplanets.  The KOI field defined by the \kepler\
team and shown on the Exoplanet Archive is stored as a floating point
number, consisting of a whole number designated to the host star
followed by a decimal portion denoting a candidate planet. For example,
KOI 102 is a star suspected to host two exoplanets, and KOI 102.01 is
the inner planet candidate and KOI 102.02 is the outer one. Once a
candidate is confirmed, the {\bf NAME} field of the planet is replaced by
the official \kepler\ ID (``Kepler" followed by a hyphen, an integer,
a space, and finally a lower case letter). The KOI number is then used as
{\bf OTHERNAME}. For more information, see
Section~\ref{sec:kepler}.

@@

Also for plotting convenience, for transiting $Kepler$ planets without
$m\sin{i}$ measured, we estimate their mass using mass-radius
relations from the literature. We follow a series of relations given
by \footnote{As of the writing of this manuscript, Kepler planet
  candidates on exoplanets.org ingested from the Exoplanet Archive
  have their masses estimated in a slightly different manner.  The
  Website uses the \citeauthor{Mordasini2012} relation for planets
  with 6$\rearth < R < b$ ($b \sim 11 \rearth$ as defined by
  \citeauthor{Mordasini2012}), the \citeauthor{Lissauer2011} relation
  between $1 \rearth < R < 6\rearth$, and $M = (1/R)^{0.306}$ in Earth
  units for planets smaller than $\rearth$.  Updating this relation to
  be consistent with the EOD (and updating the corresponding MASSREF
  fields for these candidates) is a priority upgrade for
  exoplanets.org.}

\[
M_p=
\begin{cases}
M_{\rm WM} &  R<\rearth \\
(1-x)M_{\rm WM} + xM_L  &  \rearth \leq R<4\rearth \\
M_L & 4 \rearth \leq R < 6 \rearth \\
M_M &  6\rearth \leq R < b \\
{\text \mjup} &  R \geq b
\end{cases}
\]

\noindent where $b$ is defined
below, and we use the weight $x=\left(R_{p}/\rearth-1\right)/3$ to
smoothly transition between $M_{\rm WM}$ and $M_L$ in their
overlapping regions of validity. $M_{\rm WM}$ is from \cite{Weiss2014} and is given by 
\[
\frac{M_{\rm WM}}{\mearth}=
\begin{cases}
2.69\left(\frac{R_{p}}{\rearth}\right)^{0.93} &  \rearth \leq R<1.5\rearth \\
0.582\left(0.717+\frac{R_{p}}{\rearth}\right)\left(\frac{R_{p}}{\rearth}\right)^3 &  1.5\rearth\leq R<4\rearth
\end{cases}
\]

@@

\noindent from \cite{Mordasini2012}, where
\[
\begin{tabular}{ c c c }
  & $0.1<a/{\rm AU}$ & $0.1<a/{\rm AU} \leq 1$  \\ \hline $M_0[\mearth]$ & 1756.7 & 1308.7 \\
$b[\rearth]$ & 11.684 & 11.858 \\ $w$ & 1.646 & 1.635 \\ $p$ & 2.489 & 2.849 \\ 
\end{tabular}
\]

@@

{\bf I} reports the orbital inclination of the planet. Previously,
only transiting systems had $i$ measured, but now some non-transiting
systems have dynamical or astrometric constraints on $i$ (for example,
the microlensing system OGLE-2006-BLG-109L by \citealt{Bennett2010}
and the imaged system, $\beta$ Pictoris by \citealt{Lagrange2009}).

@@

{\bf SET} is the epoch of secondary eclipse center, normally given in
BJD but (as with other fields) when the literature reports HJD or UTC
JD, we do not attempt a conversion to BJD.

@@

The {\bf SPSTAR} field previously reported the stellar type of the host
star.  We have removed it since it can be difficult to verify with
peer-reviewed references, and the field was not well maintained.  We encourage users
to use TEFF and BMV instead.

@@

We also plan to report the upper limits (XUL) for planet minimum mass (MSINI),
eccentricity (ECC), and the radial velocity semi-amplitude (K) when
the literature reports them. For example, an upper limit for ECC is
reported when the orbit is consistent with a circular one, and the
upper limit for K is reported when there is only a null result from
radial velocities. Since not all authors define the upper limits in the same
way (e.g. 1$\sigma$ or some fixed percentile), we encourage the
readers to refer to the original references for more information. We
will also include proper rendering of upper limits in the EDE Table,
proper upper limit symbols in the Plotter, and proper handling of
upper limits in filters and queries in both cases.

@@

SXW acknowledges support from the Penn State Astrobiology Research
Center, part of the NASA Astrobiology Institute. The Center for
Exoplanets and Habitable Worlds is supported by the 
Pennsylvania State University, the Eberly College of Science, and the
Pennsylvania Space Grant Consortium.

@@

@@

\bibitem[Collier Cameron et al.(2010)]{Collier Cameron2010} Collier 
Cameron, A., et al.\ 2010, \mnras, 407, 507 % WASP-33b having no RV
                                % detection and K upper limit

\bibitem[Cosentino et al.(2012)]{Cosentino2012} Cosentino, R., et al.\ 
2012, \procspie, 8446, 1V % HARPS-North

@@

\bibitem[Johnson et al.(2011)]{Johnson2011} Johnson, J.~A., et al.\ 2011, 
\apjs, 197, 26 % HD 116029B having ECC upper limit (circular orbit)

@@

\bibitem[Marcy et al.(2014)]{Marcy2014} Marcy, G.~W., et al.\ 2014, \apjs, 
210, 20 % 42 RV confirmed small Kepler planets

@@

\bibitem[Rowe et al.(2014)]{Rowe2014} Rowe, J.~F., et al.\ 2014, 
arXiv:1402.6534 % 715 new Kepler planets (multis)

@@

\bibitem[Sotin et al.(2007)]{Sotin2007} Sotin, C., Grasset, O., 
\& Mocquet, A.\ 2007, \icarus, 191, 337 % Mass-Radius for M<1Me, R<1Re

@@

SET\dotfill & Double & Epoch of secondary eclipse center in
HJD\tablenotemark{c} & -UPPER, etc. & \ref{sec:se} \\

>>>>

There are other entities devoted to similar efforts,
including the Extrasolar Planets Encyclopaedia\footnote{See
  \url{http://exoplanet.eu}.}  \citep{Schneider2011} and the NASA
Exoplanet Archive\footnote{See
  \url{http://exoplanetarchive.ipac.caltech.edu}.}
\citep{Akeson2013}.  The natures of these efforts are largely
complementary to the EOD, and to the
degree that they are redundant provide important cross-checking and
validation.  As described in \cite{Wright2011}, the EOD is
dedicated to cataloging properties of all \emph{robustly-detected} exoplanets with
\emph{well-determined} orbital parameters published in
\emph{peer-reviewed} literature, and providing outstanding data
exploration and visualization tools for these planets.

@@

{\bf KEPID} stands for KEPler IDentification, which is the integer number assigned
for a Kepler host star. KEPID is only available for unconfirmed
KOI's imported directly from the Exoplanet Archive by the
exoplanets.org backend.

{\bf KOI} stands for Kepler Object of Interest, which is an object
with transit signals detected by \kepler\ that have not been validated
as being due to exoplanets.  The KOI field defined by the \kepler\
team and shown on the Exoplanet Archive is stored as a floating point
number, consisting of a whole number designated to the host star
followed by a decimal portion denoting a candidate planet. For example,
KOI 102 is a star suspected to host two exoplanets, and KOI 102.01 is
the inner planet candidate and KOI 102.02 is the outer one. Once a
candidate is confirmed, the {\bf NAME} field of the planet is replaced by
the official \kepler\ ID (``Kepler" followed by a hyphen, an integer,
a space, and finally a lower case letter). The KOI number is then used as
{\bf OTHERNAME}. For more information, see
Section~\ref{sec:kepler}.

@@

Also for plotting convenience, for transiting $Kepler$ planets without
$m\sin{i}$ measured, we estimate their mass using mass-radius
relations from the literature. We follow a series of relations given
by
\begin{comment}
  % no longer true - already updated
\footnote{As of the writing of this manuscript, Kepler planet
  candidates on exoplanets.org ingested from the Exoplanet Archive
  have their masses estimated in a slightly different manner.  The
  Website uses the \citeauthor{Mordasini2012} relation for planets
  with 6$\rearth < R < b$ ($b \sim 11 \rearth$ as defined by
  \citeauthor{Mordasini2012}), the \citeauthor{Lissauer2011} relation
  between $1 \rearth < R < 6\rearth$, and $M = (1/R)^{0.306}$ in Earth
  units for planets smaller than $\rearth$.  Updating this relation to
  be consistent with the EOD (and updating the corresponding MASSREF
  fields for these candidates) is a priority upgrade for
  exoplanets.org.}
\end{comment}

\[
M_p=
\begin{cases}
M_{\rm WM} &  R<\rearth \\
(1-x)M_{\rm WM} + xM_L  &  \rearth \leq R<4\rearth \\
M_L & 4 \rearth \leq R < 6 \rearth \\
\min{(M_{\rm M},{\text \mjup})} &  6\rearth \leq R < b \\
{\text \mjup} &  R \geq b
\end{cases}
\]

\noindent where $b$ is defined
below, and we use the weight $x=\left(R_{p}/\rearth-1\right)/3$ to
smoothly transition between $M_{\rm WM}$ and $M_L$ in their
overlapping regions of validity. $M_{\rm WM}$ is from \cite{Weiss2014} and is given by 
\[
\frac{M_{\rm WM}}{\mearth}=
\begin{cases}
0.615\left(0.717+\frac{R_{p}}{\rearth}\right)\left(\frac{R_{p}}{\rearth}\right)^3 &  R<1.5\rearth \\
2.69\left(\frac{R_{p}}{\rearth}\right)^{0.93} &  1.5\rearth\leq R<4\rearth
\end{cases}
\]

@@

\noindent from \cite{Mordasini2012}, where
\[
\begin{tabular}{ c c c }
  & $a/{\rm AU} \leq 0.1$ & $a/{\rm AU} > 0.1$  \\ \hline $M_0[\mearth]$ & 1756.7 & 1308.7 \\
$b[\rearth]$ & 11.684 & 11.858 \\ $w$ & 1.646 & 1.635 \\ $p$ & 2.489 & 2.849 \\ 
\end{tabular}
\]

@@

The parameter {\bf I} reports the orbital inclination of the planet. Previously,
only transiting systems had $i$ measured, but now some non-transiting
systems have dynamical or astrometric constraints on $i$ (for example,
the microlensing system OGLE-2006-BLG-109L by \citealt{Bennett2010}
and the imaged system, $\beta$ Pictoris by \citealt{Lagrange2009}).

@@

\begin{comment}
{\bf SET} is the epoch of secondary eclipse center, normally given in
BJD but (as with other fields) when the literature reports HJD or UTC
JD, we do not attempt a conversion to BJD.
\end{comment}

@@

The {\bf SPTYPE} field previously reported the stellar type of the host
star.  We have removed it since it can be difficult to verify with
peer-reviewed references, and the field was not well maintained.  We encourage users
to use TEFF and BMV instead.

@@

We also plan to report the upper limits (XUL) for planet minimum mass (MSINI),
eccentricity (ECC), and the radial velocity semi-amplitude (K) when
the literature reports them. For example, an upper limit for ECC is
reported when the orbit is consistent with a circular one, and the
upper limit for K is reported when there is only a null result from
radial velocities. Since not all authors define the upper limits in the same
way (e.g. 1$\sigma$ or some fixed percentile), we encourage the
users to refer to the original references for more information. We
will also include proper rendering of upper limits in the EDE Table,
proper upper limit symbols in the Plotter, and proper handling of
upper limits in filters and queries in both cases.

@@

SXW acknowledges support from the Penn State Astrobiology Research
Center, part of the NASA Astrobiology Institute (NNA09DA76A). The Center for
Exoplanets and Habitable Worlds is supported by the 
Pennsylvania State University, the Eberly College of Science, and the
Pennsylvania Space Grant Consortium.

@@

We thank Jacob Bean for his referee report and suggestions to exoplanets.org.

@@

\bibitem[Chauvin et al.(2012)]{Chauvin2012} Chauvin, G., et al.\ 2012, 
\aap, 542, A41 % beta Pic orbital pars

%\bibitem[Collier Cameron et al.(2010)]{Collier Cameron2010} Collier 
%Cameron, A., et al.\ 2010, \mnras, 407, 507 % WASP-33b having no RV
                                % detection and K upper limit

%\bibitem[Cosentino et al.(2012)]{Cosentino2012} Cosentino, R., et al.\ 
%2012, \procspie, 8446, 1V % HARPS-North

@@

%\bibitem[Johnson et al.(2011)]{Johnson2011} Johnson, J.~A., et al.\ 2011, 
%\apjs, 197, 26 % HD 116029B having ECC upper limit (circular orbit)

@@

%\bibitem[Marcy et al.(2014)]{Marcy2014} Marcy, G.~W., et al.\ 2014, \apjs, 
%210, 20 % 42 RV confirmed small Kepler planets

@@

%\bibitem[Rowe et al.(2014)]{Rowe2014} Rowe, J.~F., et al.\ 2014, 
%arXiv:1402.6534 % 715 new Kepler planets (multis)

@@

%\bibitem[Sotin et al.(2007)]{Sotin2007} Sotin, C., Grasset, O., 
%\& Mocquet, A.\ 2007, \icarus, 191, 337 % Mass-Radius for M<1Me, R<1Re

@@

%SET\dotfill & Double & Epoch of secondary eclipse center in
%HJD\tablenotemark{c} & -UPPER, etc. & \ref{sec:se} \\
